The \dealii Library, Version 9.0

### 2018-05-16 9.0/paper.tex
Modified cache section: added compute point location information

Some of the methods in \texttt{GridTools} already use this cache to
speed up repeated calls to the same expensive methods.
\item A new \texttt{MeshWorker::mesh\_loop} function has been added that
  performs the same tasks of the \texttt{MeshWorker::loop} function without
  forcing the users to adhere to a specific interface.

>>>>

Some of the methods in \texttt{GridTools} and \texttt{FEFieldFunction} already
use this cache to avoid repeated calls to the same expensive methods.
This results in important speed-ups for computationally heavy methods like
\texttt{GridTools::compute\_point\_locations}.

\item A new \texttt{MeshWorker::mesh\_loop} function has been added that
  performs the same tasks of the \texttt{MeshWorker::loop} function without
  forcing the users to adhere to a specific interface.
